New lower bounds for Schur and weak Schur numbers

### 2021-09-20 article/introduction.tex
ws 6
nouvelles valeurs
une seule ligne State of the art

\begin{table}[H]
  \centering
\begin{NiceTabular}{*{13}{c}}[vlines]
\CodeBefore
	\cellcolor{gray!40}{2-2}
	\cellcolor{gray!40}{2-3}
	\cellcolor{gray!40}{2-4}
	\cellcolor{gray!40}{2-5}
	\cellcolor{gray!40}{2-6}
	\cellcolor{gray!40}{3-2}
	\cellcolor{gray!40}{3-3}
	\cellcolor{gray!40}{3-4}
	\cellcolor{gray!40}{3-5}
	\cellcolor{gray!40}{3-6}
\Body
	\hline
	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
	\hline
	\Block{2-1}{Before Rowley} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,680 & 5\,041 & 15\,124 & 51\,120 & 172\,216 & 575\,664 \\
	& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{Fredricksen} & \cite{AbbottHanson} & \cite{AbbottHanson} & 
		\cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
	\hline
	Rowley & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & 
		\Block{2-1}{5\,286} & \Block{2-1}{17\,694} & \Block{2-1}{60\,320} & \Block{2-1}{201\,696} & \Block{2-1}{631\,840} \\
	\cite{RowleyRamsey} & & & & & & & & & & & & \\
	\hline
	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{638\,548} \\
	\hline
\end{NiceTabular}
\caption{Comparison of lower bounds for Schur numbers}
\label{table:1}
\end{table}

\begin{table}[H]
  \centering
\begin{NiceTabular}{*{13}{c}}[vlines]
\CodeBefore
	\cellcolor{gray!40}{2-2}
	\cellcolor{gray!40}{2-3}
	\cellcolor{gray!40}{2-4}
	\cellcolor{gray!40}{2-5}
	\cellcolor{gray!40}{3-2}
	\cellcolor{gray!40}{3-3}
	\cellcolor{gray!40}{3-4}
	\cellcolor{gray!40}{3-5}
\Body
	\hline
	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
	\hline
	\Block{2-1}{Before Rowley} & 2 & 8 & 23 & 66 & 196 & 582 & 1\,740 & 5\,201 & 15\,596 & 51\,520 & 172\,216 & 575\,664 \\
	& & & & & \cite{ELIAHOU2012175} &\cite{EliahouBook} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & \cite{Rafilipojaona} & 
		\cite{AbbottHanson} & \cite{AbbottHanson} & \cite{AbbottHanson} \\
	\hline
	Rowley & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{} & \Block{2-1}{642} & \Block{2-1}{2\,146} & 
		\Block{2-1}{6\,976} & \Block{2-1}{21\,848} & \Block{2-1}{70\,778} & \Block{2-1}{241\,282} & \Block{2-1}{806\,786} \\
	\cite{RowleyWS} & & & & & & & & & & & & \\
	\hline
	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{22\,536} & \textbf{71\,214} & \textbf{243\,794} & \textbf{815\,314} \\
	\hline
\end{NiceTabular}
\caption{Comparison of lower bounds for weak Schur numbers}
\label{table:2}
\end{table}

>>>>

\begin{table}[H]
  \centering
\begin{NiceTabular}{*{13}{c}}[vlines]
\CodeBefore
	\cellcolor{gray!40}{2-2}
	\cellcolor{gray!40}{2-3}
	\cellcolor{gray!40}{2-4}
	\cellcolor{gray!40}{2-5}
	\cellcolor{gray!40}{2-6}
	\cellcolor{gray!40}{3-2}
	\cellcolor{gray!40}{3-3}
	\cellcolor{gray!40}{3-4}
	\cellcolor{gray!40}{3-5}
	\cellcolor{gray!40}{3-6}
\Body
	\hline
	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
	\hline
	\Block{2-1}{State of the art} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,696 & 5\,286 & 17\,694 & 60\,320 & 201\,696 & 637\,856 \\
	& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{rowley2021improved} & \cite{RowleyRamsey} & \cite{RowleyRamsey} & 
		\cite{RowleyRamsey} & \cite{RowleyRamsey} & \cite{RowleyRamsey} \\
	\hline
	\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{644\,628} \\
	\hline
\end{NiceTabular}
\caption{Comparison of lower bounds for Schur numbers}
\label{table:1}
\end{table}

\begin{table}[H]
  \centering
\begin{NiceTabular}{*{13}{c}}[vlines]
\CodeBefore
	\cellcolor{gray!40}{2-2}
	\cellcolor{gray!40}{2-3}
	\cellcolor{gray!40}{2-4}
	\cellcolor{gray!40}{2-5}
	\cellcolor{gray!40}{3-2}
	\cellcolor{gray!40}{3-3}
	\cellcolor{gray!40}{3-4}
	\cellcolor{gray!40}{3-5}
\Body
	\hline
	\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
	\hline
	\Block{2-1}{State of the art} & 2 & 8 & 23 & 66 & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 & 241\,282 & 806\,786 \\
	& & & & & \cite{ELIAHOU2012175} &\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & 
		\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} \\
	\hline
	\hyperref[Schur]{\textbf{Our results}}  & & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
	\hline
\end{NiceTabular}
\caption{Comparison of lower bounds for weak Schur numbers}
\label{table:2}
\end{table}
